% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[twocolumn, 11pt
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Hot Mutant Vigilantes},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Hot Mutant Vigilantes}
\author{by Mr. Zech (\href{https://mrzech.itch.io}{mrzech.itch.io})}
\date{}

\begin{document}
\maketitle

\hypertarget{premise}{%
\subsection{Premise}\label{premise}}

YOU ARE A HOT MUTANT VIGILANTE.

You are a student at a school for gifted youngsters where the
extra-curricular activities involve dressing up in spandex and defending
the world. The school has zero legal authority to do this, hence the
label `vigilante'. The government and the humans hate you.

This work is a hack of \href{https://gshowitt.itch.io/sexy-battle-wizards}{Grant
Howitt's Sexy Battle Wizards}, created for
\href{https://itch.io/jam/hot-mutant-summer-jam}{the Hot Mutant Summer
Jam} and directly inspired by the X-men.

\hypertarget{character-creation}{%
\subsection{Character Creation}\label{character-creation}}

Why are you so Hot? (d6)

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Literal abs of steel
\item
  Majestic mutton chops beard
\item
  The form-fitting spandex shows off your butt
\item
  Impeccable bone structure
\item
  Daddy / Hot mama
\item
  Dangerous rebel with a cool jacket
\end{enumerate}

What is your vigilante specialty? (d6)

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Pilot / Driving
\item
  Tracking / Scouting
\item
  Negotiation / Deception
\item
  Hacking
\item
  Science / Gadgetry
\item
  Martial Arts
\end{enumerate}

\newpage

What is your Mutation? (d20)

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Concussive eye beams
\item
  Walk through walls
\item
  Short-range teleportation
\item
  Telepathy
\item
  Shapeshifting
\item
  Angel wings
\item
  Beast form
\item
  Healing factor
\item
  Sonic scream
\item
  Power absorption through contact
\item
  Explosive projectiles
\item
  Pyrotechnics
\item
  Organic metal
\item
  Super luck
\item
  Magnetism
\item
  Illusionist
\item
  Stretching
\item
  Weather manipulation
\item
  Telekinesis
\item
  Speedster
\end{enumerate}

You have three stats. Assign 1, 2 and 3 to each of your stats.\\
\textbf{HOT!} Charm baddies with your skin-tight spandex-clad hot
body.\\
\textbf{MUTANT!} Unleash your mutant superpower.\\
\textbf{VIGILANTE!} Fight crime without the approval of the law.

\newpage

\hypertarget{rolling-dice}{%
\subsection{Rolling Dice}\label{rolling-dice}}

When you act to gain an advantage or solve a difficult problem, roll a
number of six-sided dice equal to the most relevant stat. Spend
determination (see below) on a 1-for-1 basis to add additional dice to
the pool.

If your higest dice
\begin{itemize}	
\item beats the difficulty, you succeed.
\item is equal to the difficulty, you succeed, gain 1 stress and the GM tells you something
bad that happens. 
\item is lower than the difficulty, you fail, gain 1 stress and 1
determination and the GM tells you something bad that happens.
\end{itemize}

Stress represents your overall condition, including physical injury,
fatigue and emotional conditions like anger or embarrassment.

When you fail, if your total final stress is higher than the highest
dice rolled, decide with the GM how you are taken out of the scene. Some
possibilities are your character passes out, is physically thrown out,
or your character runs away.

\hypertarget{gm-section}{%
\subsection{GM Section}\label{gm-section}}

Give the players an inkling of what the first, obvious disaster is, and
let them go at it.

The difficulty of a task is related to the \textbf{impact of success},
not the complexity of the task.\\
4: standard stuff with standard results\\
5: Audacious or risky stuff with great impact\\
6: Clutch, against-the-odds stuff that can really turn the tide of the
situation

If an NPC isn't kissable, think ``Could I make them kissable?''

What's going wrong? (Roll twice; one disaster hides another much more
dangerous disaster)

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  A fellow student's mutation is out of control
\item
  Mutant terrorist are trying to assassinate a mutant-hating senator
\item
  The principal of the school is missing
\item
  An underground commune of mutants is under attack
\item
  A mutant-loving/hating cult has formed
\item
  The location of the government's secret mutant facility is discovered
\end{enumerate}

What's this place like?

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  a sterile environment of mutant science
\item
  a military town attached to the largest anti-mutant base
\item
  on a living mutant island
\item
displaced from the time stream
\item
 an anti-mutant march at the Capital
\item
a sleepaway summer camp in a creepy forest
\end{enumerate}

Who's going to stand in our way? (Roll twice)

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  A sexy Alien Monarch and their army
\item
  The government's inexplicably sexy mutant-hunting robots
\item
  The principal's sexy Mutant rival
\item
  A sexy cyborg out for revenge
\item
  A sexy time traveller intent on ``fixing the timeline''
\item
  The sexy mutant who was expelled from the school last year
\end{enumerate}

\end{document}
